%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Padmapiyush}{Pathak}{ \urlstyle{same}\href{http://padmapiyush.github.io}{padmapiyush.github.io} | 
\href{mailto:thepadmapiyush@gmail.com}{thepadmapiyush@gmail.com}| \\
\href{tel:+91 9532683568}{+91 9532683568}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Galgotias College of Engineering and Technology}
\descript{MCA}
\location{July 2024 | Greater Noida, IND}
\sectionsep

\subsection{Integral University}
\descript{BCA}
\location{July 2022 | Lucknow, IND}
\location{ Cum. GPA: 8.36 / 10 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/padmapiyush}{\bf Padmapiyush} \\
LinkedIn://  \href{https://www.linkedin.com/in/padmapiyush}{\bf padmapiyush} \\
YouTube://  \href{https://www.youtube.com/@padmapiyush}{\bf @padmapiyush} \\
Twitter://  \href{https://twitter.com/piyush_gayatri}{\bf @piyush\_gayatri}\\
Leetcode://  \href{https://leetcode.com/padmapiyush}{\bf padmapiyush}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Software Engineering \\
Distributed Database Systems \\
Big Data \\
Data Analytics \\
Cloud Computing \\
Machine Learning \\
Artificial Intelligence \\
\sectionsep

\subsection{Undergraduate}
Data Structures \& Algorithm \\
Design and Analysis of Algorithm \\
Object Oriented Programming \\
Operating Systems \\
Database Management System \\
Computer Networks \\
Mathematics  I, II  \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Experienced:}
Java \textbullet{} Python  \\
\location{Intermediate:}
Microsoft Excel \textbullet{} HTML \textbullet{} CSS \textbullet{} JavaScript \textbullet{} Numpy \textbullet{} Pandas \textbullet{} Linux \textbullet{} Tableau \textbullet{}  SQL \textbullet{} Git \\
\location{Familiar:}
Google Cloud Platform  \textbullet{} Android \textbullet{} MySQL \textbullet{}  Node.js 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}
\runsubsection{Google Cloud Platform (GCP) Essential Training for Developers}
\descript{| LinkedIn }
\location{May 2023}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Explored data storage and database management with Cloud Storage and Cloud SQL.
\item Gained comprehensive insights into cloud computing principles and practices. 
\item Utilized GCP resources effectively, resulting in reduction in cloud expenses.
\end{tightemize}
\sectionsep

\runsubsection{Introduction to Data Science in Python}
\descript{| DataCamp }
\location{Feb 2023}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mastered fundamental Python programming for data analysis.
\item Explored data manipulation using Pandas.
\item Gained proficiency in data visualization with Matplotlib and Seaborn
\end{tightemize}
\sectionsep

\runsubsection{Google Data Analytics Certificate}
\descript{| Coursera }
\location{July 2022}
\begin{tightemize}
\item Gained proficiency in data analysis, data visualization, and data-driven decision-making.
\item Achieved a score of 96\% in the final assessment, showcasing a strong grasp of course material.
\item Successfully completed 3 real-world data analysis projects to apply learned concepts.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project}
\runsubsection{Forecast sales revenue}
\location{Feb 2023 – Mar 2023 }
\begin{tightemize}
\item Developed a robust machine learning model using Python and scikit-learn to forecast sales revenue.
\end{tightemize}
\sectionsep

\runsubsection{Sentiment analysis using NLP}
\location{Jan 2023 – Feb 2023}
\begin{tightemize}
\item Developed a sentiment analysis model using Natural Language Processing (NLP) techniques to accurately classify emotions expressed in text data.
\end{tightemize}
\sectionsep

\runsubsection{Visualizing air pollutants}
\location{Sep 2022}
\begin{tightemize}
\item Developed an interactive Tableau dashboard showcasing air pollution trends across major cities worldwide.

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteer Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Position of Responsibility} 
\textbullet{} \textbf{Placement Coordinator(MCA, GCET)}: Resoponsible for all placement related activities within my department at GCET.\\
\textbullet{} \textbf{CoLead(CodeOn)}: Led as a CoLead for the CodeOn (Department Coding Community) and designed over 3 Newsletters for it.\\
\textbullet{} \textbf{Tech Lead(MCA)}: Led my department in GCET in various Hackathons and Technical Events.\\
\textbullet{} \textbf{Member(GDSC)}: Member of Google Developers Student Club in GCET.
\end{minipage} 
\end{document}  \documentclass[]{article}
